---
title: "RepGreene_Data_analysis"
author: "lynde"
date: '2022-12-07'
output: pdf_document
---

```{r include=FALSE, eval=TRUE}
library("knitr")
library("janitor")     
library("broom.mixed") 
library("lme4")
library("emmeans")
library("tidyverse")
library("afex")
library("report")
library("readr")
theme_set(theme_classic())
```

## Data Review Motivation

Here I describe the intended analysis

using lmer 

```{r loading}
setwd("~/F.Replications/Replications/Greene_Rep")
pilot_a_data <- read_csv("Data/pilot_a_data.csv")
View(pilot_a_data)
```

## Wringle Wrangle 

Make new data frames that are tidy such that I can run the analysis more cleanly. 
variables i need, the choices, yes/no, the RT

The names of the variables I need to pull 
prolific_id
vitamins /all the names of the questions (12, block 6 v 6 )
timing page submit


```{r wrangling, echo=FALSE}
df.data = clean_names(pilot_a_data) 


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
