---
title: "RepGreene_Data_analysis"
author: "lynde"
date: '2022-12-07'
output: pdf_document
---
##Libaries libraries
```{r include=FALSE, eval=TRUE}
library("knitr")
library("janitor")     
library("broom.mixed") 
library("lme4")
library("emmeans")
library("tidyverse")
library("afex")
library("report")
library("readr")
library("qualtRics")

theme_set(theme_classic())
```

## Data Review Motivation

We're trying to replicate the main finding which will involve running a series of linear models and ultimately a linear mixed effect model. First will be looking at effect of load on judgement and we shouldn't see significance. Then effect of load on utilitarian vs deontological choice each. This should, if replicated, demonstrate a significant effect on utilitarian judgments only. 


##Loading
```{r loading}
setwd("~/F.Replications/Replications/Greene_Rep")

pilot_a_data <- read_csv("Data/pilot_a_data.csv")
View(pilot_a_data)

raw_data_pilot_a <- read_survey("pilot_a_data.csv", legacy = TRUE)
view(raw_data_pilot_a)

```
## Wringle Wrangle 

Make new data frames that are tidy such that I can run the analysis more cleanly. 
variables I need, the choices, yes/no, the RT

The names of the variables I need to pull 
prolific_id
vitamins /all the names of the questions (12, block 6 v 6 )
timing page submit

gonna do some select and long-ing. 

```{r wrangling, echo=FALSE}
df.data = clean_names(pilot_a_data) 


```


## Run some basic diagnostics

Histogram of the RT load/no load
Set the standard deviation for stun (at 2SD)
 
```{r basics, echo=FALSE}



```

## Gimme some linear models please

###First up the set of linear models that should not be significant. 


```{r modeling, echo=FALSE}



```

###Glimmer limmer 
```{r modeling, echo=FALSE}



```

Results




