---
title: "RepGreene_Data_analysis"
author: "lynde"
date: '2022-12-07'
output:
  pdf_document: default
  html_document:
    df_print: paged
---
##Libaries libraries
```{r include=FALSE, eval=TRUE}
library("knitr")
library("janitor")     
library("broom.mixed") 
library("lme4")
library("emmeans")
library("tidyverse")
library("afex")
library("report")
library("readr")
library("qualtRics")
library("reshape2")
library("DataExplorer")
library("sjPlot")
library("sjmisc")
library("ggplot2")
library("modelbased")
library("esquisse")
theme_set(theme_bw())
```

##Motivation

We're trying to replicate the main finding which will involve running a series of linear models and ultimately a linear mixed effect model. First will be looking at effect of load on judgement and we shouldn't see significance. Then effect of load on utilitarian vs deontological choice each. This should, if replicated, demonstrate a significant effect on utilitarian judgments only. 

Original Author's findings
"There was no main effect of load (F(1, 83.2) = 2.29, p = .13). There was a margin- ally significant main effect of judgment (F(1, 71.7) = 3.9, p = .052), with longer RT for utilitarian judgments (LS Means (SEM) ms: utilitarian = 6130 (207), non-utili- tarian = 5736 (221)). Critically, we observed the predicted interaction between load and judgment (F(1, 62.9) = 8.5, p = .005). (See Fig. 1.) Planned post hoc contrasts revealed a predicted increase in RT for utilitarian judgment under load (F(1, 106.3) = 9.8, p = .002; LS Means (SEM) ms: load = 6506 (238), no load = 5754 (241)), but no difference in RT for non-utilitarian judgment resulting from load (F(1, 169.6) = .10, p = .75; LS Means: load = 5691 (264), no load = 5781 (261)). Utilitarian judgments were slower than non-utilitarian judgments under load (p = .001), but there was no such effect in the absence of load (p = .91). This general pattern also held when item, rather than participant, was modeled as a random effect, although the results in this analysis were not as strong. There was no effect of load on judgment (v2(1, N = 82) = .24, p = .62), with 61% utilitarian judgments under load (95% CI: 57–66%) and 60% (95% CI: 55–64%) in the absence of load"

##Loading
```{r loading}
setwd("~/F.Replications/Replications/Greene_Rep/Data")

# pilot_a_data <- read_csv("Data/pilot_a_data.csv")
# View(pilot_a_data)
# 
# raw_data_pilot_a <- read_survey("pilot_a_data.csv", legacy = TRUE)
# view(raw_data_pilot_a)

raw_data <- read_survey("Greene_08_Rep_121422.csv", legacy = TRUE) %>%
  clean_names()
```
## Wringle Wrangle 

Make new data frames that are tidy such that I can run the analysis more cleanly. 
variables I need, the choices, yes/no, the RT

The names of the variables I need to pull 
prolific_id
vitamins /all the names of the questions (12, block 6 v 6 )
timing page submit


iv load 
for each choice and load are my predictors for "last click"
marginal effects lsmean 

"t1_l1_timing_vitamin_first_click",
"t2_l1_timing_sub_first_click",     
"t3_l1_timing_sac_first_click",
"t4_l1_timing_modlb_first_click",
"t5_l1_timing_lawara_first_click",
"t6_l1_timing_euthan_first_click",
"t1_l2_timing_cryb_first_click",
"t2_l2_timing_foot_first_click",
"t3_l2_timing_modbm_first_click",
"t4_l2_timing_modsaf_first_click",
"t5_l2_timing_soph_first_click",
"t6_l2_timing_vacc_first_click"

"t1_l1_vitamins",
"t2_l1_sub",                   
"t3_l1_sac",                    
"t4_l1_modlb",                
"t5_l1_lawara",             
"t6_l1_euthan",                 
"t1_l2_cryb",           
"t2_l2_foot",                     
"t3_l2_modbm",                 
"t4_l2_modsaf",               
"t5_l2_soph",                      
"t6_l2_vacc",                      
gonna do some select and long-ing. 

```{r wrangling, echo=FALSE}
#grab the variables I want
df.data <- select(raw_data,
                  "prolific_id",
                  contains("l1"),
                  contains("l2"),
                  -contains("page_submit"),
                  -contains("last_click"),
                  -contains("click_count")) 
#remove the pilot & qualtrics headers that I don't want
df.data <- df.data %>% 
  filter(prolific_id !="beth")%>% 
  filter(prolific_id !="kate") %>% 
  filter(prolific_id !="ImportId") %>% 
  filter(prolific_id !="test001_JWB") %>% 
  filter(prolific_id !="asdf") %>% 
  filter(prolific_id != '{"ImportId":"QID33_TEXT"}') 

#I think I'll use these later  
conditions <- c("load" = "L2",
                "no load" = "L1")
choices <- c("utilitarian" = 1,
             "not utilitarian" = 2)
#make some variables of the names of variables.....
variables <- variable.names(df.data)
trialvar <- c("t1_l1_vitamins","t2_l1_sub",                   "t3_l1_sac", "t4_l1_modlb", "t5_l1_lawara", "t6_l1_euthan", "t1_l2_cryb", "t2_l2_foot","t3_l2_modbm","t4_l2_modsaf", "t5_l2_soph", "t6_l2_vacc")
trialrt <- c("t1_l1_timing_vitamin_first_click", "t2_l1_timing_sub_first_click", "t3_l1_timing_sac_first_click", "t4_l1_timing_modlb_first_click", "t5_l1_timing_lawara_first_click", "t6_l1_timing_euthan_first_click", "t1_l2_timing_cryb_first_click", "t2_l2_timing_foot_first_click", "t3_l2_timing_modbm_first_click", "t4_l2_timing_modsaf_first_click", "t5_l2_timing_soph_first_click", "t6_l2_timing_vacc_first_click")

#Tried to Melt rather than Pivot...

# df.datalongval <- melt(
#   df.data,
#   "prolific_id",
#   c(trialvar),
#   na.rm = TRUE)
# 
# df.datalongrt <- melt(
#   df.data,
#   "prolific_id",
#   c(trialrt),
#   na.rm = TRUE)
# 
# df.datalongee <- left_join(df.datalongval, df.datalongrt, by = "prolific_id", keep = FALSE) %>% view()
# 
# df.datalongee1 <- df.datalongee %>% 
#   mutate(condload = (variable.x ("l2")))
# 
# df.datalongee <-df.datalongee %>% 
#   rename(trialname = variable.x) %>% 
#   rename(choice = value.x) %>% 
#   rename()

#...I give up....

df.datalong <- df.data %>% 
  group_by("prolific_id") %>% 
  pivot_longer(
    cols = !"prolific_id",
    names_to = c("trial", "load"),
    names_sep = "_",
    values_to = "choice"
  ) 
df.datalong <- df.datalong %>% 
  filter(choice != "prolific_id" )

#stuck, it's just slightly tooooo long
```

Got some help from Anna Xu to move the data around into where I want it.
Anna noticed that the rows are every other so rather than trying to do another pivot she just kinda...moved the line around.

```{r chunk by anna, echo=TRUE}
odd.ind <- seq_len(nrow(df.datalong)) %% 2
df.datalong.odds <- df.datalong[odd.ind == 1, ]
df.datalong.evens <- df.datalong[odd.ind == 0, ]

df.datalong.odds$bin.choice <- df.datalong.evens$choice

df.datalong
df.datalong.odds

new.df.datalong <- df.datalong.odds

df.datalong <-new.df.datalong %>% 
  rename(rt = "bin.choice") %>% 
  view()
```
YAY long!

## Run some basic descriptives?

We still need to do a little more organizing then peak at the data. 

```{r basics, echo=FALSE}
df.datalong <-df.datalong %>% 
  mutate(rtnum = as.numeric(rt)) %>% 
  mutate(choicenum = as.factor(choice)) 

#histo of the RT
df.datalong %>% 
  ggplot(mapping = aes(rtnum)) +
  geom_histogram(bins = 10)

#lets tease out the histos from each condition, l1 is no load, l2 is load
fig1 <- df.datalong %>% 
  filter(load == "l1") %>% 
  ggplot(mapping = aes(choice, rtnum))+
  geom_violin(color = "purple", 
                fill = "purple",
              alpha = 0.9)+
  labs(title = "no load")
  
fig2 <- df.datalong %>% 
  filter(load == "l2") %>% 
  ggplot(mapping = aes(choice, rtnum))+
  geom_violin()+
  labs(title = "load")

fig1 
fig2

```
Ever notice violins look like rorschach blots?

### We should probably trim the RT
From the violins above we can see that there's probably a ton of outlier RTs.

```{r more descriptives, echo =TRUE}
#trim my rts from the data & get standard devs
sumsdfdatalong <- df.datalong %>% 
  group_by(load) %>% 
  summarize(rtmean = mean(rtnum),
            stdrtmean = 2*sd(rtnum),
            minrt = rtmean-stdrtmean,
            maxrt = rtmean+stdrtmean)

minrt <- sumsdfdatalong$minrt
maxrt <- sumsdfdatalong$maxrt

#lets trim this to two sd like original authors
df.datalongtrim <- df.datalong %>% 
  group_by(load) %>% 
  filter(rtnum > minrt) %>% 
  filter(rtnum < maxrt)

#making a report bc why not
#rep.dfdlongtrim <- create_report(df.datalongtrim)
#rep.dfdlong <- create_report(df.datalong)
# ^^^^ uncoment to run 

#I want a good-game-plot as well
df.datalongtrim %>% 
  ggplot(mapping = aes(x = load,
         y = rtnum,
         fill = choicenum
        ))+
  geom_violin()+
  labs(title = "Effect of Load and Moral Choice on RT",
       x = "Load Conditions",
       y = "Response Time Means (seconds)")+
  scale_x_discrete(labels=c("l1" = "No Load",
                            "l2" = "Load"))+
  scale_fill_discrete(name="Choice type",
                  labels=c("1" = "Utilitarian",
                           "2" = "Not Utilitarian"))
```

## Model model model!

Going to do three linear models.
Always doing prolific id-- the participant-- as a random effect. 

Model 1:Choice on RT

Model 2:Load on RT

Model 3:The big kahuna! Load * choice (on RT)!

```{r model time, echo=TRUE}
#modeling choice
m1<- lmer(rtnum ~choicenum +(1|prolific_id),
          data = df.datalongtrim)
report(m1) 
summary(m1)

#modeling load 
m2 <- lmer(rtnum ~load +(1|prolific_id),
           data = df.datalongtrim)
report(m2)
summary(m2)

#model the load*choice and rt
m3 <- lmer(rtnum ~load *choicenum +(1|prolific_id),
           data = df.datalongtrim)
report(m3)
summary(m3)

#looking at model comparisons
anova(m2, m3)
anova(m1, m2)
anova(m1, m3)

#early peek at the model
plot_model(m3, type = "int")

#save model outputs to make a figure
means <- estimate_means(m3)

as.factor(means$load) #this will make the graphing easier

#trying to use a different package to graph the model
plot_model(m3, type = "int",
           axis.title = "Mean RT (s)",
           colors = "gs",
           legend.title = "Choice Type",
           title = "The effect of cognitive load on RT")

#fuck it I'm gonna do ggplot 
means %>% 
  ggplot(mapping = aes(x = load,
                       y = Mean,
                       group = choicenum,
                       color = choicenum
                        ))+
  geom_line(size = 1.5)+
  geom_errorbar(aes(ymin=CI_low, ymax=CI_high), width=.05, size = 0.6)+
  geom_point()+
  labs(title = "Effect of Load and Moral Choice on RT",
       x = "Load Conditions",
       y = "Response Time Means (seconds)")+
  scale_x_discrete(labels=c("l1" = "No Load",
                            "l2" = "Load"))+
  scale_colour_grey(name="Choice type",
                  labels=c("1" = "Utilitarian",
                           "2" = "Not Utilitarian"),
                  start = 0.3,
                  end = 0.7
                  )

#tada!
```

Soooo this is not great huh. Seems like (a) rt significantly increases as a function of load irrespective of choice type. Frankly I'm not suprised. Further, we did not replicate the selective interference effect on utilitarian choices. Womp womp. 
 
Time to write up the report!

```{r, echo=F}
sessionInfo()
```
